---
title: "Lab 4 Presentation"
#subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Robinpreet Dhillon"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

## Introduction

Creating slides with **xaringan** has its advantages such as it allows us to embed R markdown instead of just plain markdown, it supports LaTeX, as well as R code blocks. The following few slides demonstrate these basic functionalities. 

---
name: colors

## Fenced Markdown code block

These are really useful to provide separate long lines of code from the rest of the text. Below, the fenced code block from Q6 is shown again:
```{verbatim, lang = "markdown"}
title: "Lab 4 - Introduction to RStudio and R Markdown. Presentations"
output:
  html_document:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
author: "Robinpreet Dhillon"
date: "October 1, 2022"
```
The distinction is immediately visible and allows emphasis on the block.
---

## Adding Numbers

R Code Blocks can be evaluated and displayed on the same slide. Below, a basic addition of two numbers is shown and outputted:

```{r, eval=TRUE}
x = 10
y = 10
z = x + y
z
```

---

## Subtracting Numbers

Similarly, a simple function is written that takes two numbers and subtracts them. 

```{r}
sub_nums <- function(x, y){
  z = x - y
  return(z)
}
sub_nums(10, 1)
```

---
class: center, middle

# Thanks!

Slides created via the R packages:

[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
